### 2021-09-17 docs/paper/sections/0_abstract.tex
Rework first sections (up to approach)

	In the dependency graph of a software ecosystem, \emph{downstream dependencies} are the nodes that depend on a package.
	Other than for upstream dependencies, solutions that provide individual package developers with this kind of information do not yet exist.
	This paper makes two major contributions:
	\begin{enumerate*}[label=(\roman*)]
		\item We propose an approach for mining usage data about npm packages from their downstream dependencies by utilizing a static type analyzer.
		\item We introduce a tool that allows package developers to survey usage samples of their APIs by incorporating the aggregated usage data into an integrated development environment.%
			\footnote{
				All artifacts are available on GitHub under the following URL: \url{https://github.com/LinqLover/downstream-repository-mining}
				\TODO{Insert name and use link to VSCE}
			}
	\end{enumerate*}
	We find that usage data from downstream dependency repositories are a promising source of information for mining software repositories and that they can be useful to support package developers in improving or extending their APIs.

>>>>

	In the dependency graph of a software ecosystem, \emph{downstream dependencies} are the nodes that depend on a package.
	Other than for upstream dependencies, solutions that provide individual package developers with this kind of information rarely exist to date.
	This paper makes two major contributions:
	\begin{enumerate*}[label=(\roman*)]
		\item We propose an approach for mining usage data about packages from their downstream dependencies by utilizing a static type analyzer.
		\item We introduce a tool that allows npm package developers to survey usage samples of their APIs by incorporating the aggregated usage data into an integrated development environment.%
			\footnote{
				All artifacts are available on GitHub under the following URL: \url{https://github.com/LinqLover/downstream-repository-mining}
				\TODO{Insert name and use link to VSCE}
			}
	\end{enumerate*}
	We find that usage data from downstream dependency repositories are a promising source of information for mining software repositories and that they can be useful to support package developers in improving or extending their APIs.

### 2021-09-17 docs/paper/sections/1_introduction.tex
Rework first sections (up to approach)

Despite this connectedness by design, however, the development process of many packages is still characterized by an isolated approach:
While OSS developers commonly submit tickets to or contribute patches against \emph{upstream repositories} that they depend on to solve subproblems, the reverse direction of these edges -- called \emph{downstream dependencies} -- is often neglected by package developers when they extend, restructure, or refactor their solutions.
This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces, unidentified defects, and compatibility problems \citep[see][]{bogart2015breaks}.\TODO{do we need to prove each of this?}
Eventually, all these issues impair the capabilities of the global OSS community to build and support faultless products in an efficient process.
In the following, downstream dependencies will also be referred to shortly as \emph{dependencies}.

>>>>

Despite this connectedness by design, however, the development process of many packages is still characterized by an isolated approach:
While OSS developers commonly submit tickets to or contribute patches against \emph{upstream repositories} that they depend on to solve subproblems, the reverse direction of these edges -- called \emph{downstream dependencies} -- is often neglected by package developers when they extend, restructure, or refactor their solutions.
This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces, unidentified defects, and compatibility problems \citep[see][]{bogart2015breaks}.\TODO{do we need to prove each of this?}
Eventually, all these issues impair the capabilities of the global OSS community to build and support high-quality products.
In the following, downstream dependencies will also be referred to shortly as \emph{dependencies}.

### 2021-09-17 docs/paper/sections/2_related_work.tex
Rework first sections (up to approach)

However, existing research about dependency graphs primarily takes a broad statistical perspective, and researchers often rely on a large corpus of downloaded software repositories \citep{abdalkareem2017developers,katz2020libraries,kikas2017structure}.
% and researchers usually either access certain package registries such as the npm registry that already contain bidirectional dependency data, or they collect large amounts of software repositories from development platforms such as GitHub, extract dependency lists from each repository's metadata, and finally invert all adjacency lists to get the downstream dependencies.
As opposed to this approach, these capacities will not be appropriate for scenarios that are occasionally performed by developers of a single package only.
In this case, developers will often use a public \emph{code search} service such as GitHub code search\footnote{\url{https://docs.github.com/en/github/searching-for-information-on-github}} or Sourcegraph\footnote{\url{https://sourcegraph.com/}} instead.
\citet{liu2020opportunities} survey current methods and trends in code search tools that include, besides simple full-text search, newer approaches such as structural or semantic search queries, code similarity metrics, or Machine Learning methods.

@@

Dependency graphs do not provide information about package usage on a finer granularity, so reference insights about single package members such as classes or methods remain unknown.
The process of extracting fine-granular information about all references to individual elements of an interface is often referred to as \emph{API usage analysis}.
A simple approach to this problem is to perform a string search for package names or members in the dependencies \citep{mileva2010mining}.
\citet{qiu2016understanding} propose a more elaborated approach that operates on the AST of each parsed dependency to avoid false positive matches that can be caused by ambivalent identifier names.
A very similar approach is also chosen by \citet{sawant2017fine} who evaluate the collected usage data in order to analyze the historical importance of certain features supported by an API.

@@

To bring together dependency graphs and call graphs, \emph{ecosystem call graphs} can be constructed by applying call graphs to entire ecosystems, crossing repository boundaries.
\citet{hejderup2018software} propose an approach to do so for the JavaScript/npm ecosystem in which they also model the semantic version numbers of packages and perform an impact analysis for vulnerabilities based on their graph.
\citet{nielsen2021modular} elaborate on this work by developing a call graph generator tailored to this problem that comes with significant improvements in terms of recall and performance; a very similar method is also sketched by \citet{boldi2020fine}.
\citet{wang2020empirical} describe a similar approach for the same ecosystem and apply it to the domain of locating security issues in a project's upstream dependencies.
With \caps{Pr\"azi}, \citet{hejderup2021praezi} also describe their implementation of a dependency-scale call graph for the Rust/Cratesio ecosystem in-depth.
For Java/Maven, \citet{keshani2021scalable} proposes another solution.

@@

To establish an adequate developer experience, any collected usage data still need to be presented in a suitable manner.
A common approach for this is a hierarchical and navigatable representation of the collected call tree.
The first form of this representation has been invented as the ``message set'' tool for browsing senders and implementors in an object-oriented system for the Smalltalk programming environment \citep[section~10.1f.]{goldberg1984smalltalk}.
Modern alternatives include the \caps{Stacksplorer} \citep{karrer2011stacksplorer} or \caps{Blaze} \citep{kramer2012blaze} that list next to the currently focused method other methods which are adjacent to this method in the call graph.
With a focus on exploring references to API members, \citet{de2013multi} propose a set of additional views, including hierarchical lists and word clouds for highly referenced identifiers.
Focusing on exploring APIs in a non-code-centric way, \citet{hora2015apiwave} propose a dashboard that allows developers to browse existing APIs and track possibly breaking changes in their interfaces.

>>>>

However, existing research about dependency graphs primarily takes a broad statistical perspective, and researchers often rely on a large corpus of downloaded software repositories \citep{abdalkareem2017developers,katz2020libraries,kikas2017structure}.
As opposed to this approach, these capacities will not be appropriate for scenarios that are occasionally performed by developers of a single package only.
In this case, developers will often use a public \emph{code search} service such as GitHub code search\footnote{\url{https://docs.github.com/en/github/searching-for-information-on-github}} or Sourcegraph\footnote{\url{https://sourcegraph.com/}} instead.
\citet{liu2020opportunities} survey current methods and trends in code search tools that include, besides simple full-text search, newer approaches such as structural or semantic search queries, code similarity metrics, or Machine Learning methods.

@@

Dependency graphs do not provide information about package usage on a finer granularity, so reference insights about single package members such as classes or methods remain unknown.
The process of extracting fine-granular information about all references to individual elements of an interface is often referred to as \emph{API usage analysis}.
A simple approach to this problem is to perform a string search for package names or members in the dependencies \citep{mileva2010mining}.
\citet{qiu2016understanding} propose a more elaborated approach that operates on the \emph{abstract syntax tree} (AST) of each parsed dependency to avoid false positive matches that can be caused by ambivalent identifier names.
A very similar approach is also chosen by \citet{sawant2017fine} who evaluate the collected usage data in order to analyze the historical importance of certain features supported by an API.

@@

To bring together dependency graphs and call graphs, \emph{ecosystem call graphs} can be constructed by applying call graphs to entire ecosystems, crossing repository boundaries.
\citet{hejderup2018software} propose an approach to do so for the JavaScript/npm ecosystem in which they also model the semantic version numbers of packages and perform an impact analysis for vulnerabilities based on their graph; a very similar method is described by \citet{boldi2020fine} to formulate the vision of new design for package management systems that provides options for finer-granular reuse of solutions.
\citet{nielsen2021modular} elaborate on this work by developing a call graph generator tailored to this problem that comes with significant improvements in terms of recall and performance.
\citet{wang2020empirical} describe a similar approach for the same ecosystem and apply it to the domain of locating security issues in a project's upstream dependencies.
With \caps{Pr\"azi}, \citet{hejderup2021praezi} also describe their implementation of a dependency-scale call graph for the Rust/Cratesio ecosystem in-depth.
For Java/Maven, \citet{keshani2021scalable} proposes another solution.

@@

To establish an adequate developer experience, any collected usage data still need to be presented suitably.
A common approach for this is a hierarchical and navigatable representation of the collected call tree.
The first form of this representation has been invented as the interactive ``message set'' tool for browsing senders and implementors in an object-oriented system for the Smalltalk programming environment \citep[section~10.1f.]{goldberg1984smalltalk}.
Modern alternatives include the \caps{Stacksplorer} \citep{karrer2011stacksplorer} or \caps{Blaze} \citep{kramer2012blaze} that list next to the currently focused method other methods which are adjacent to this method in the call graph.
With a focus on exploring references to API members, \citet{de2013multi} propose a set of additional views, including hierarchical lists and word clouds for highly referenced identifiers.
Focusing on exploring APIs in a non-code-centric way, \citet{hora2015apiwave} propose a dashboard that allows developers to browse existing APIs and track possibly breaking changes in their interfaces.
